Poincar\'e--Friedrichs constants over triangulated domains

### 2024-05-02 main.tex
more updates

We gather notions of simplicial meshes for the subsequent discussion. 
Apart from basic definitions and notational conventions, we pay special attention to the question of when a simplicial complex is a triangulation of a manifold. 
A particularly important class of simplicial complexes are so-called \emph{shellable} complexes. Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. While shellable complexes are a very special class of complexes, they faciliate achieving the main goal of our exposition.
Our main references on simplicial complexes and shellability are the monographs by Ziegler~\cite{ziegler2012lectures} and Kozlov~\cite{kozlov2008combinatorial}.

@@

We now collect examples for Poincar\'e--Friedrich inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align}
In addition to that,
according to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{ENT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{\rm{ENT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
The constant $C_{\rm{ENT},p}$ is the best possible. 
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{1-\frac 2 p}C_{\rm{ENT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case.

\begin{remark}
    Let us compare the different estimates for the Poincar\'e inequality in the case $2 \leq p$. 
    We observe 
    \begin{align*}
        2^{1-\frac 2 p}
        C_{\rm{ENT},p}
        =
        2 
        \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 4^{\frac 1 p} }
        =
        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  \sqrt[p]{p-1}  }
        \leq 
        \frac{ p \sin(\pi/p) }{ 4^{\frac 1 p} \pi  }
        \leq 
        \frac{1}{ 4^{\frac 1 p} }
        .
    \end{align*}
    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden} for $p \geq 2$.
    In the limit as $p$ goes to $1$, \eqref{math:esposito:poincare} recovers \eqref{math:acostaduran}. 
    In the limit as $p$ goes to infinity, \eqref{math:esposito:poincare} implies the Poincar\'e inequality 
    \begin{align*}
        \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
        \leq 
        \diam(\Omega)
        \| \nabla u \|_{L^{\infty}(\Omega)}
        ,
        \quad
        u \in W^{1,\infty}(\Omega)
        %
    \end{align*}
    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
    Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
%     Taking the \emph{informal} limit also suggest the inequality 
%     \begin{align*}
%         \min\limits_{ c \in \bbR }
%         \| u - c \|_{L^{\infty}(\Omega)}
%         \leq 
%         \frac{d}{2}
%         \| \nabla u \|_{L^{\infty}(\Omega)}
%         ,
%         \quad
%         u \in W^{1,\infty}(\Omega)
%         ,
%     \end{align*}
%     however, we generally cannot exchange the minimum and the limit, so that is strictly informal. 
\end{remark}

\begin{align}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    % 2^{ - \frac{p-1}{p}}
    %2^{ - 1 + \frac{1}{p}}
    \frac{1}{ 2^{ 1 - \frac{1}{p} } }
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
% d/2 in the case $p = 1$ over convex domains

@@

\begin{proof}
    Given $z \in \Omega$, we define 
    \[
        u_z(x) := \int_0^1 \bff( z + t(x-z) ) \cdot (x-z)
    \]
\end{proof}

@@

% either proceeding simplex by simplex, matching along faces 
% or proceeding patch by patch, matching over intersections
\begin{theorem}
    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
\end{theorem}

@@

 Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j < m$ such that $F_m := T_m \cap T_j$ is a face of dimension $n-1$. We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.

@@

 Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j}$. 
 Since $\nabla u_{F_{m}|T_j} = \nabla w_{m-1|T_j}$,
 there exists a constant $c_{m} := w_{m-1|T_j} - u_{F_{m}|T_j}$.
 We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_j} = w_{m-1|T_j}$. 
 But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
 As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
 Moreover, 
 \begin{gather*}
    \| u'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \qquad 
    \| c_{m} \|_{L^{p}(T_m)}
    \leq 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_j)},
    \\ 
    \| c_{m} \|_{L^{p}(T_j)}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_j)} + \| u_{F_{m}} \|_{L^{p}(T_j)} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
    \| u_{F_{m}} \|_{L^{p}(T_j)}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_j)}
    .
 \end{align*}
 In the special case $p < \infty$, we also find 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
    &\leq 
    3^{p-1}
    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m) }{ \vol(T_j) }
    \| u_{F_{m}} \|_{L^{p}(T_j)}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
    \\&\leq 
    3^{p-1}
    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_j) } \right)
    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m) }{ \vol(T_j) }
    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
    .
 \end{align*}
 Recursive application provides the desired result. 
\end{proof}

@@

>>>>

We gather notions of simplicial meshes for the subsequent discussion. 
Apart from basic definitions and notational conventions, we pay special attention to the question of when a simplicial complex is a triangulation of a manifold. 
A particularly important class of simplicial complexes are so-called \emph{shellable} complexes. Such simplicial complexes are constructed by successively adding simplices in a particularly well-behaved manner. While shellable complexes are a very special class of complexes, they facilitate achieving the main goal of our exposition.
Our main references on simplicial complexes and shellability are the monographs by Ziegler~\cite{ziegler2012lectures} and Kozlov~\cite{kozlov2008combinatorial}.

@@

We now collect examples for Poincar\'e--Friedrichs inequalities for important special cases; see also~\cite[Lemma~3.24]{ern2021finite} for a short overview. Over convex bounded domains, it is known~\cite{bebendorf2003note,acosta2004optimal} that 
\begin{align}\label{math:acostaduran}
    \| u - u_{\Omega} \|_{L^{1}(\Omega)}
    \leq 
    \frac{\diam(\Omega)}{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    ,
    \\
    \| u - u_{\Omega} \|_{L^{2}(\Omega)} \label{math:bebendorf}
    \leq 
    \frac{\diam(\Omega)}{\pi}
    \| \nabla u \|_{L^{2}(\Omega)}
    ,
    \quad 
    u \in W^{1,2}(\Omega)
    .
\end{align}
These two estimates are the best possible in the cases $p=1$ and $p=2$, respectively, in terms of the diameter alone. 
Moreover, when $1 < p < \infty$, we know~\cite{chua2006estimates} that
\begin{align}\label{math:chuawheeden}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm CW},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{{\rm CW},p} 
    := 
    \sup\limits_{ v \in C^\infty([0,1]) \setminus \bbR } 
    \frac{ 
        \| v - v_{[0,1]} \|_{L^{p}([0,1])} 
    }{ 
        \| \nabla v \|_{L^{p}([0,1])} 
    }
    \leq 
    \sqrt[p]{p} 2^{1-\frac 1 p}
    =
    2
    \left( \frac p 2 \right)^{\frac 1 p}
    .
\end{align}
In addition to that,
according to~\cite{ferone2012remark,esposito2013poincare}, when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{ENT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where 
\begin{align}
    C_{\rm{ENT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
The constant $C_{\rm{ENT},p}$ is the best possible. 
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{\rm{ENT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
The main feature in proving these results is that the best constant in the Poincar\'e inequality is already the constant in the $1$-dimensional case.

\begin{remark}
    Let us compare the different estimates for the Poincar\'e inequality.
    In the case $2 \leq p$, 
    \begin{align*}
        2^{1-\frac 2 p}
        C_{\rm{ENT},p}
        =
        \frac{ 2^{1-\frac 2 p} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        =
        4^{-\frac 1 p}
        \leq
        C_{{\rm CW},p} 
        .
    \end{align*}
    In the case $2 \geq p$, 
    \begin{align*}
        2^{\frac 2 p - 1}
        C_{\rm{ENT},p}
        =
        \frac{ 2^{\frac 2 p - 1} }{2}
        \frac{ \sin(\pi/p) }{ \pi/p }
        \frac{ 1 }{ \sqrt[p]{p-1} }
        \leq
        \frac{ 2^{\frac 2 p-1} }{2}
        =
        2^{\frac 2 p - 2}
        =
        4^{\frac 1 p - 1}
        \leq
        C_{{\rm CW},p} 
%         % 
%         .
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} \cdot 2 }
%         =
%         4^{\frac 1 p}
%         \frac{ p \sin(\pi/p) }{ 4\pi \sqrt[p]{p-1} }
%         \leq 
%         \frac 1 2
        .
    \end{align*}
    It follows that \eqref{math:esposito:poincare} is tighter estimate than \eqref{math:chuawheeden} for $1 < p < \infty$.
    In the limit as $p$ goes to $1$, \eqref{math:esposito:poincare} recovers \eqref{math:acostaduran}. 
    In the limit as $p$ goes to infinity, \eqref{math:esposito:poincare} implies the Poincar\'e inequality 
    \begin{align*}
        \| u - u_{\Omega} \|_{L^{\infty}(\Omega)}
        \leq 
        \diam(\Omega)
        \| \nabla u \|_{L^{\infty}(\Omega)}
        ,
        \quad
        u \in W^{1,\infty}(\Omega)
        %
    \end{align*}
    because the $L^{\infty}$-norm is the limit of the $L^{p}$-norm. 
    Of course, this Poincar\'e inequality implies a Poincar\'e--Friedrichs inequality with the same constant. 
%     Taking the \emph{informal} limit also suggest the inequality 
%     \begin{align*}
%         \min\limits_{ c \in \bbR }
%         \| u - c \|_{L^{\infty}(\Omega)}
%         \leq 
%         \frac{d}{2}
%         \| \nabla u \|_{L^{\infty}(\Omega)}
%         ,
%         \quad
%         u \in W^{1,\infty}(\Omega)
%         ,
%     \end{align*}
%     however, we generally cannot exchange the minimum and the limit, so that is strictly informal. 
\end{remark}

% https://www.ams.org/journals/proc/2004-132-01/S0002-9939-03-07004-7/S0002-9939-03-07004-7.pdf
% d/2 in the case $p = 1$ over convex domains

@@

\color{Emerald}
\begin{align}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    % 2^{ - \frac{p-1}{p}}
    %2^{ - 1 + \frac{1}{p}}
    \frac{1}{ 2^{ 1 - \frac{1}{p} } }
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}

\begin{proof}
    Given $z \in \Omega$, we define 
    \[
        w(x,z) 
        := 
        \int_0^1 \bff( z + t(x-z) ) \cdot (x-z)
        =
        u(x) - u(z)
        .
    \]
    Subsequently,
    \begin{align*}
        w(x) = |\Omega|^{-1} \int_{\Omega} w(x,z) dz.
    \end{align*}
    Clearly, $\nabla_{x} u(x) = \nabla_{x} w(x,z) = \nabla_{x} w(x)$.
    Next, 
    \begin{align*}
        \int_{\Omega} | w(x) |^{p} dx
        &\leq 
        \int_{\Omega} |\Omega|^{-1} \int_{\Omega} | w(x,z) |^{p} dz dx
        \\&\leq 
        \int_{\Omega} |\Omega|^{-1} \int_{\Omega} \int_0^1 | \bff( z + t(x-z) ) \cdot (x-z) |^{p} dz dx
        \\&= 
        |\Omega|^{-1} \int_{\Omega} \int_{\Omega} \int_0^{D/|x-z|} | \bff( z + t(x-z) ) \cdot (x-z) |^{p} dz dx
        .
    \end{align*}

\end{proof}
\color{black}

@@

% either proceeding simplex by simplex, matching along faces 
% or proceeding patch by patch, matching over intersections

\begin{lemma}
    Let $T_1$ and $T_{2}$ be two $n$-simplices such that $F = T_1 \cap T_2$ is a common subsimplex of dimension $n-1$. Then 
    \color{red} Here we estimate the Poincar\'e constant over a face patch.
\end{lemma}
\begin{proof}
    \color{red}
    Possible approaches: 
    \begin{itemize}
     \item Take the trace jump (requires trace inequality with explicit constant) and extend the resulting constant function
     \item The union is star-shaped with respect to some (hopefully large) convex set, then use inequality for that situation (available in literature)
     \item Reflection trick
     \item Paper by Veeser and Verfuerth?
    \end{itemize}
    Most importantly, all constants must be explicitly computable!
    We can do all these methods and compare the results. 
    \color{black}
    We write $U := T_1 \cup T_2$. Let $u \in W^{1,p}(U)$.
    Suppose $u_1 \in W^{1,p}(T_1)$ and $u_2 \in W^{1,p}(T_2)$
    satisfy $\nabla u_1 = \nabla u_{|T_1}$ and $\nabla u_2 = \nabla u_{|T_2}$.
    Then there exists a constant $c \in \bbR$ such that $c = \trace_{T_1,F} u_1 - \trace_{T_1,F} u_2$.
    Consequently, if we define 
    \color{red} yet to be completed.
\end{proof}

The following result by Veeser and Verfürth~\cite[Lemma 2.8]{veeser} is important in this context.

\begin{lemma}\label{lemma:traceinequality}
    Let $p \in [1,\infty)$ and let $T$ be an $n$-dimensional simplex with a face $F$. Then 
    \begin{align*}
        |F|^{-1} \| u \|_{L^{p}(F)}^{p}
        \leq 
        |T|^{-1} \| u \|_{L^{p}(T)}^{p}
        +
        p \cdot \diam(T) |T|^{-1} 
        \| u \|_{L^{p}(T)}^{p-1}
        \| \nabla u \|_{\bfL^{p}(T)}
        .
    \end{align*}
\end{lemma}

\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
    \color{red}Precise form of the inequality yet to be discussed, though the construction principle is clear.
\end{theorem}

@@

 Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$. We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.

@@

 Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
 Since $\nabla u_{F_{m}|T_{j(m)}} = \nabla w_{m-1|T_{j(m)}}$,
 there exists a constant $c_{m} := w_{m-1|T_{j(m)}} - u_{F_{m}|T_{j(m)}}$.
 We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_{j(m)}} = w_{m-1|T_{j(m)}}$. 
 But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
 As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
 Moreover, 
 \begin{gather*}
    \| u'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \qquad 
    \| c_{m} \|_{L^{p}(T_m)}
    \leq 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_{j(m)})},
    \\ 
    \| c_{m} \|_{L^{p}(T_{j(m)})}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_{j(m)})} + \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
    .
 \end{align*}
 In the special case $p=1$,
 \begin{align*}
    \| w_{m} \|_{L^{1}(T_m)}
    \leq 
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } 
    \right)
    \| u_{F_m} \|_{L^{1}(U_{F_m})}
    +
    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
    \| w_{m-1}\|_{L^{1}(T_{j(m)})}
    .
 \end{align*}
 In the special case $p=\infty$, we get 
 \begin{align*}
    \| w_{m} \|_{L^{\infty}(T_m)}
    \leq 
    2
    \| u_{F_m} \|_{L^{\infty}(U_{F_m})}
    +
    \| w_{m-1}\|_{L^{\infty}(T_{j(m)})}
    .
 \end{align*}
 In particular, letting $q$ be the complementary exponent, 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    \leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} } \right)^{\frac 1 q}
    \left( 
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        +
        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
    \right)^{\frac 1 p}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
    .
 \end{align*}

 \color{red}We want to summarize the Lp norms so that the Poincare inequality over $U_F$ is applied only once. In the special cases $p=1$ and $p=\infty$, this works as above. Do we have a formula for general $p$ that contains these as limit cases? \color{black}
 In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
    &\leq 
    3^{p-1}
    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
    \\&\leq 
    3^{p-1}
    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m) }{ \vol(T_{j(m)}) }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
    ,
 \end{align*}
 and therefore
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    3^{\frac{p-1}{p}}
    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)^{\frac 1 p}
    \| u_{F_m} \|_{L^{p}(U_{F_m})} 
    +
    3^{\frac{p-1}{p}}
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
    .
 \end{align*}
 \color{blue}
 In the special case $p < \infty$, we use the finite-dimensional H\"older inequality to find 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
    &\leq 
    \left( 
        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
    \right)^{ p-1 }
    \left( 
        \| u_{F_m} \|_{L^{p}(T_m)}^{p}
        +
        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}^{p}
        +
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
    \right)
    ,
 \end{align*}
 and therefore
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \left( 
        1 + 2 \frac{ \vol(T_m)^{\frac{1}{p-1}} }{ \vol(T_{j(m)})^{\frac{1}{p-1}} }
    \right)^{ \frac{p-1}{p} }
    \left( 
        \| u_{F_m} \|_{L^{p}(T_m)} 
        +
        \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
        +
        \| w_{m-1}\|_{L^{p}(T_{j(m)})} 
    \right)
    .
 \end{align*}
 \color{black}
 Recursive application provides the following estimate:
 if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
 such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
 then 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        3^{\frac{p-1}{p}}
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{j(l)})^{\frac 1 p} }
    \right)
    \max\left( 1, \frac{ \vol(T_t) }{ \vol(T_{j(t)}) } \right)^{\frac 1 p}
    \| u_{F_t} \|_{L^{p}(U_{F_t})}
    \\&\quad \quad \quad 
    +
    \left( 
        \prod_{t < l \leq m} 
        3^{\frac{p-1}{p}}
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{j(l)})^{\frac 1 p} }
    \right)
    \| u_{T_0}\|_{L^{p}(T_{0})}
    .
 \end{align*}

\end{proof}

@@

\begin{figure}
\begin{tikzpicture}
    % Define the vertices of the triangles
    \coordinate (A) at (0,0);
    \coordinate (B) at (2,0);
    \coordinate (C) at (1,1.5);
    \coordinate (D) at (3,1.5); % Extra vertex for the second triangle
    \coordinate (E) at (3,2.5); % Extra vertex for the second triangle
    \coordinate (F) at (4,0.25); % Extra vertex for the second triangle
    \coordinate (X) at (1,-1.5);
    \coordinate (Y) at (3,-1.5); % Extra vertex for the second triangle

    \coordinate (CentroidABC) at ($(A)!0.3333!(B)!0.3333!(C)$);
    \coordinate (CentroidBCD) at ($(B)!0.3333!(C)!0.3333!(D)$);
    \coordinate (CentroidCDE) at ($(C)!0.3333!(D)!0.3333!(E)$);
    \coordinate (CentroidBDF) at ($(B)!0.3333!(D)!0.3333!(F)$);
    \coordinate (CentroidABX) at ($(A)!0.3333!(B)!0.3333!(X)$);
    \coordinate (CentroidBXY) at ($(Y)!0.3333!(B)!0.3333!(X)$);
    \coordinate (CentroidBFY) at ($(Y)!0.3333!(B)!0.3333!(F)$);

    % Draw triangles
    \draw[fill=gray!20] (A) -- (B) -- (C) -- cycle; 
    \draw[fill=gray!30] (B) -- (C) -- (D) -- cycle; 
    \draw[fill=gray!30] (C) -- (D) -- (E) -- cycle; 
    \draw[fill=gray!30] (B) -- (D) -- (F) -- cycle; 
    \draw[fill=gray!20] (A) -- (B) -- (X) -- cycle; 
    \draw[fill=gray!20] (Y) -- (B) -- (X) -- cycle; 
    \draw[fill=gray!20] (Y) -- (B) -- (F) -- cycle;

    % Draw arrows between triangle centroids
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidBCD); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidCDE); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBCD) -- (CentroidBDF); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABC) -- (CentroidABX); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidABX) -- (CentroidBXY); 
    \draw[-latex, thick, shorten <=2.5pt, shorten >=2.5pt] (CentroidBXY) -- (CentroidBFY);

    % Labels for vertices (optional)
    \node at (A) [below left] {$A$};
    \node at (B) [below right] {$B$};
    \node at (C) [above] {$C$};
    \node at (D) [above right] {$D$};
\end{tikzpicture}
\caption{Strongly connected triangulation of a domain. The arrows depict a tree in the strong connection graph of the form used in Theorem~\ref{theorem:poincarefriedrichsestimate:grad}.}
\end{figure}

\newpage
